---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# IsoMemo

<!-- badges: start -->
[![R-CMD-check](https://github.com/Pandora-IsoMemo/isomemo-data/workflows/R-CMD-check/badge.svg)](https://github.com/Pandora-IsoMemo/isomemo-data/actions)
<!-- badges: end -->

IsoMemo is a Big Data initiative bringing together isotopic data from archaeology, ecology, and environmental & life sciences. Isotopic tracers are used across a variety of research fields to provide a rich diversity of scientific information, but lack of centralized storage limits efficient data use. The IsoMemo initiative brings together independent repositories of isotopic data within the fields of archaeology, ecology, and environmental & life sciences. The goals of the initiative are to make isotopic data easily findable and accessible so that it can be easily reused for research purposes. IsoMemo also promotes the creation of data standards and interoperability with other types. Within IsoMemo each independent database self-manages and curates their data and defines metadata requirements. However, the initiative also promotes the creation of networks linking different databases.

This R package to retrieve data from Max-Planck-Institute (MPI) IsoMemo Web-application API and publish on CRAN for public download. For more information and access all IsoMemo Apps: <https://isomemoapp.com/>

*Isomemo Project Director:* 

* Dr. Ricardo Fernandes:  <fernandes@shh.mpg.de>
- Max Planck Institute for the Science of Human History. School of Archaeology (University of Oxford)

*Developer*: INWT Statistics GmbH 

* API developer: Andreas Neudecker, INWT <andreas.neudecker@inwt-statistics.de>
* Maintainer: Jianyin Roachell, INWT <jianyin.roachell@inwt-statistics.de>


## Installation

You can install the released version of IsoMemo from [CRAN](https://CRAN.R-project.org) with:

```{r installation}
install.packages("IsoMemo")
```

And the development version from [GitHub](https://github.com/) with:
```{r dev}
options(repos = c(getOption("repos"), PANDORA = "https://Pandora-IsoMemo.github.io/drat/"))
install.packages("IsoMemo")
```
## Example of how to use the package:

```{r example}
options(repos = c(getOption("repos"), PANDORA = "https://Pandora-IsoMemo.github.io/drat/"))
install.packages("IsoMemo")

library(IsoMemo)
## basic example code
df = getData(db="IntChron")
head(df)

# with category argument
df = getData(db="IntChron",category = "Location")
head(df)

# with field argument
df = getData(db="LiVES",category = "Location",field= "latitude")
head(df)
```





